---
title: "JHPiego sim"
author: "JHBC"
date: "2025-02-07"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    code_folding: show
    html_document:
      keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(data.table)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(readxl)
library(tidyr)

set.seed(123)
```
# Approach

In this document I walk through my simulation of interventions. The current document focuses on preeclampsia.

All the parameters here can be tweaked. I've made judgments about what I think work best. 

# Simulation Parameters

## Population ANC in Kenya, Nigeria, India, and Senegal

This is drawn from the provided spreadsheet. Place that file in this folder with the name 'model-inputs.xls'.

```{r n_population, echo=FALSE, message=FALSE}

model_inputs <- readxl::read_excel("model-inputs.xlsx", sheet = "DRAFT Inputs")

n_population <- model_inputs |> 
  filter(Parameter == "# women in individual ANC in project per year") |> 
  mutate(
    Kenya = as.numeric(Kenya),
    Nigeria = as.numeric(Nigeria),
    India = as.numeric(India),
    Senegal = as.numeric(Senegal),
    n = Kenya + Nigeria + India + Senegal
  ) |> 
  pull(n)

n_population |> kable()

```

## Beta Distribution

We use **Beta distributions** to model uncertainty in key parameters like the **proportion of women reached**, **intervention uptake**, and the **probability of adverse events**. The Beta distribution is ideal for modeling probabilities, as it is defined on the interval \([0, 1]\).

The Beta distribution is parameterized by **\(\alpha\)** and **\(\beta\)**, with the mean given by:

\[
\mu = \frac{\alpha}{\alpha + \beta}
\]

To ensure consistency and parsimony across models, we fix **\(\alpha\)** in the range at 40 and calculate **\(\beta\)** based on the target probability \( p \):

\[
\beta = \alpha \times \left( \frac{1 - p}{p} \right)
\]

This approach results in **fairly tight distributions** centered around the target probability. For **low probabilities**, the distribution is slightly **right-skewed**, while for **high probabilities**, it becomes **left-skewed**. However, the skewness remains minimal, ensuring the distribution remains concentrated around the specified mean. This method provides a standardized, reliable way to represent uncertainty across various parameters.

```{r beta_calc, echo=FALSE}
# Function to calculate beta given alpha and target probability
calculate_beta_params <- function(alpha, target_prob) {
  beta <- alpha * ((1 - target_prob) / target_prob)
  
  # Return as a list
  return(list(alpha = alpha, beta = beta))
}

# Function to generate alpha-beta pairs for all probabilities (0 to 100%)
generate_all_beta_params <- function(alpha, step_size = 0.01) {
  probabilities <- seq(0.01, 0.99, by = step_size)  # Avoid 0 and 1 to prevent infinite beta values
  
  params <- lapply(probabilities, function(p) {
    beta <- alpha * ((1 - p) / p)
    return(data.frame(probability = p, alpha = alpha, beta = beta))
  }) |> bind_rows()
  
  return(params)
}

```

### Beta-distribution Simulation Assumptions

Assuming a fixed **\(\alpha = 40\)**, we calculate the corresponding **\(\beta\)** for the following key parameters. When a range is provided, we center the beta distribution around the midpoint.

### Population Reached

* Aspirin: Provided parameters: 13-16% of ANC: assumption: **14.5%** of the population reached
* Calcium: Provided parameters: 100% of ANC: assumption: **100%** of the population reached
* MgSO₄: Provided parameters: 5% of ANC: assumption: **5%** of the population reached
* MMS: Provided parameters: 100% of ANC: assumption: **100%** of the population reached
* FCM: Provided parameters: 12% of ANC: assumption: **12%** of the population reached
* ASA: Provided parameters: 11% of ANC: assumption: **11%** of the population reached
* MMS: Provided parameters: 11% of ANC: assumption: **11%** of the population reached

### Adverse Event Incidence

* Aspirin, Preeclampsia: Provided parameters: 10-20%: assumption: **15%** incidence
* Aspirin, Eclampsia, Provided parameters: 1-2%: assumption: **1.5%** incidence
* MgSO₄, Eclampsia, Provided parameters: 1-2%: assumption: **1.5%** incidence
* MMS: Anemia: Provided parameters: 40%: assumption: **40%** incidence
* MMS: Low birth weight: 13.7-16.1%: assumption: **14.9%** incidence
* FCM, Moderate and Severe Anemia: Provided parameters: 12%: assumption: **12%** incidence

### Intervention Uptake

* Aspirin, Preeclampsia/Eclapmsia: Provided parameters: 75%: assumption: **75%** uptake
* MGSO₄, Eclampsia: Provided parameters: 50-80%: assumption: **65%** uptake
* MMS Anemia/LBW: Provided parameters: 75%: assumption: **75%** uptake
* FCM, Anemia: Provided parameters: 85%: assumption: **85%** uptake


To model uncertainty around these estimates, we use **Beta distributions** with a fixed **\(\alpha = 40\)** and calculate the corresponding **\(\beta\)** to match the expected proportion for each intervention.


```{r show_beta_dists, echo=FALSE, message=FALSE, warning=FALSE}
alpha_fixed <- 40

# Function to calculate beta given alpha and target probability
calculate_beta_params <- function(alpha, target_prob) {
  beta <- alpha * ((1 - target_prob) / target_prob)
  return(beta)
}

# Combined dataset for Population Reached, Adverse Event Incidence, and Intervention Uptake
simulation_data <- data.frame(
  category = c(
    rep("Population Reached", 5),
    rep("Adverse Event Incidence", 6),
    rep("Intervention Uptake", 4)
  ),
  drug_condition = c(
    "Aspirin", "Calcium", "MgSO₄", "MMS", "FCM",                       # Population Reached
    "Aspirin (Preeclampsia)", "Aspirin (Eclampsia)", "MgSO₄ (Eclampsia)", 
    "MMS (Anemia)", "MMS (Low Birth Weight)", "FCM (Anemia)",          # Adverse Event Incidence
    "Aspirin (PE/Eclampsia)", "MgSO₄ (Eclampsia)", 
    "MMS (Anemia/LBW)", "FCM (Anemia)"                                # Intervention Uptake
  ),
  target_prob = c(
    0.145, 1.00, 0.05, 1.00, 0.12,                                    # Population Reached
    0.15, 0.015, 0.015, 0.40, 0.149, 0.12,                            # Adverse Event Incidence
    0.75, 0.65, 0.75, 0.85                                            # Intervention Uptake
  )
)

# Calculate beta values
simulation_data <- simulation_data |> 
  mutate(beta = calculate_beta_params(alpha_fixed, target_prob))

# Create a new combined label for facet titles
simulation_data <- simulation_data |> 
  mutate(facet_label = paste0(drug_condition, "\n(", category, ", ", round(target_prob * 100, 1), "%)"))

# Generate Beta samples for each intervention
samples <- simulation_data |> 
  rowwise() |> 
  mutate(proportion = list(rbeta(10000, alpha_fixed, beta))) |> 
  unnest(proportion)

# Combined Plot
ggplot(samples, aes(x = proportion, fill = category)) +
  geom_histogram(bins = 50, alpha = 0.6, position = "identity", color = "black") +
  geom_vline(data = simulation_data, aes(xintercept = target_prob), 
             linetype = "dashed", color = "red", linewidth = 1) +
  facet_wrap(~facet_label, scales = "free_y", ncol = 3) +
  labs(title = "Beta Distributions for Population Reached, Adverse Event Incidence, and Intervention Uptake",
       x = "Proportion", y = "Frequency") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1)) +
  theme_minimal() + 
  theme(legend.position = "none",
        strip.text = element_text(size = 10, face = "bold"))

```


## Effect sizes

For effect sizes, when given a range, we will assume a uniform distrubtion with minimum and upward bounds. When only a single percent is provided, we do 10% on each side. If a CI is provided from research, we use that.

* Aspirin, Preeclampsia: Provided parameters: 10-24%; assumption: 10-24%
* Calcium, Preeclampsia: Provided parameters: 50%; assumption: 40-60%
* MgSO₄, Eclampsia: Provided parameters: 46%; assumption: 36-56%
* MMS, Anemia: Provided parameters: 27%; assumption: 17-37%
* FCM, Anemia: Provided parameters: 75%; assumption from CI: 64-87%



# Simulation Steps
## Simulation Steps Description

We simulate the intervention and its potential benefits using probabilistic methods to account for uncertainty. We will run **3,000,000 simulations** for each scenario, with flexibility to scale this number for higher precision in future analyses.

---

### 1. **Population Initialization**
The total population of women in antenatal care (**ANC**) is fixed at the sum of women estimated in **Kenya**, **Nigeria**, **India**, and **Senegal**. Based on current data, this totals **422,726** women.

---

### 2. **Simulating Population Reached**
The proportion of women who can be reached by the intervention is drawn from a **Beta distribution**. We fix:

\[
\alpha = 40, \quad \beta = \alpha \times \left(\frac{1 - p}{p}\right)
\]

Where **\( p \)** is the target proportion of the population expected to be reached.

**For example**, if we estimate that **15%** of the population is reachable (\( p = 0.15 \)):

\[
\beta = 40 \times \left(\frac{1 - 0.15}{0.15}\right) = 40 \times 5.6667 \approx 226.67
\]

Thus, the proportion of the population reached is drawn from **Beta(40, 226.67)**.

---

### 3. **Simulating Intervention Uptake**
Among those reached, the proportion of women who uptake the intervention is also drawn from a **Beta distribution** using the same formula:

\[
\alpha = 40, \quad \beta = 40 \times \left(\frac{1 - p}{p}\right)
\]

**For example**, if we estimate **75%** uptake (\( p = 0.75 \)):

\[
\beta = 40 \times \left(\frac{1 - 0.75}{0.75}\right) = 40 \times 0.3333 \approx 13.33
\]

Thus, intervention uptake is drawn from **Beta(40, 13.33)**.

---

### 4. **Simulating Adverse Event Probability**
The baseline probability of experiencing the adverse event (**preeclampsia**) without intervention is modeled using a **Beta distribution** with:

\[
\alpha = 40, \quad \beta = 40 \times \left(\frac{1 - p}{p}\right)
\]

**For example**, if the estimated incidence is **15%** (\( p = 0.15 \)):

\[
\beta = 40 \times \left(\frac{1 - 0.15}{0.15}\right) = 226.67
\]

Thus, the adverse event probability is drawn from **Beta(40, 226.67)**, allowing for variability around the baseline incidence.

---

### 5. **Effect Size Simulation**
The **effect size** (i.e., the reduction in the adverse event rate due to the intervention) is drawn from a **uniform distribution** when a range is provided:

\[
\text{Uniform}(p_{\text{min}}, p_{\text{max}})
\]

**For example**, if the effect size is estimated to reduce preeclampsia by **10% to 24%**, we use:

\[
\text{Uniform}(0.10, 0.24)
\]

This assumes equal likelihood across the entire range of plausible effect sizes.

---

### 6. **Adverse Events Without Intervention**
For those **not receiving** the intervention, adverse events are simulated using a **binomial distribution** based on the adverse event probability drawn in step 4:

\[
\text{Binomial}(n_{\text{no intervention}}, p_{\text{adverse event}})
\]

**For example**, if **300,000** women do not receive the intervention and the adverse event probability is drawn as **14%**, we simulate:

\[
\text{Binomial}(300,000, 0.14)
\]

---

### 7. **Adverse Events With Intervention**
For those **receiving** the intervention, the adverse event probability is reduced by the **effect size** from step 5. Adverse events are simulated using:

\[
\text{Binomial}\left(n_{\text{uptake}}, p_{\text{adverse event}} \times (1 - \text{effect size})\right)
\]

**For example**, if the baseline adverse event rate is **15%** and the effect size is drawn as **20%**, the adjusted rate becomes:

\[
p_{\text{adjusted}} = 0.15 \times (1 - 0.20) = 0.12
\]

We then simulate adverse events using **Binomial(\(n_{\text{uptake}}\), 0.12)**.

---

### 8. **Calculating Cases Prevented**
The number of **cases prevented** is calculated as the difference between the **expected cases without intervention** and the **observed cases with intervention**:

\[
\text{Cases Prevented} = \left(n_{\text{uptake}} \times p_{\text{adverse event}}\right) - \text{Adverse Events With Intervention}
\]

**For example**, if **50,000** women received the intervention, and the baseline adverse event rate is **15%**, we expect:

\[
50,000 \times 0.15 = 7,500 \text{ cases without intervention}
\]

If the intervention reduces cases to **6,000**, then:

\[
\text{Cases Prevented} = 7,500 - 6,000 = 1,500
\]

---

### **Summary of Simulation Approach**

For each simulation, we do **not assume fixed values** for the reachable population, intervention uptake, adverse event rates, or effect sizes. Instead, we draw from **Beta distributions** (with **\(\alpha = 40\)** and appropriately calculated **\(\beta\)**) and **uniform distributions** to reflect uncertainty. This allows us to describe both the **distribution of potential outcomes** and their **mean estimates**, offering a robust assessment of intervention impact.

# Simulation Results

```{r simulation_functions, echo=FALSE}

simulate_outcomes <- function(
  population_size = 422726,
  n_simulations = 3000000,

  # Alpha Parameter for Beta Distributions
  alpha_param = 40,  # Default alpha = 40

  # Target Probabilities for Reached, Uptake, and Adverse Event
  target_p_reached = 0.15,        # Example: 15% reachable population
  target_p_uptake = 0.75,         # Example: 75% intervention uptake
  target_p_adverse_event = 0.15,  # Example: 15% adverse event rate without intervention

  # Effect Size Range
  effect_size_min = 0.10,
  effect_size_max = 0.24,

  # Caching
  simulation_name = "default_simulation",
  attempt_cache = FALSE
) {
  # Ensure results directory exists
  if (!dir.exists("results")) {
    dir.create("results")
  }

  cache_path <- paste0("results/", simulation_name, "_", n_simulations, "_sims.rds")

  cat("Starting simulation...\n")
  cat("Total simulations: ", format(n_simulations, scientific = FALSE), "\n")

  # Check for cached results
  if (attempt_cache && file.exists(cache_path)) {
    cached_data <- readRDS(cache_path)
    return(cached_data)
  }

  # Function to calculate beta based on alpha and target probability
  calculate_beta <- function(alpha, p) {
    beta <- alpha * ((1 - p) / p)
    return(beta)
  }

  # Calculate beta values for each parameter
  beta_reached <- calculate_beta(alpha_param, target_p_reached)
  beta_uptake <- calculate_beta(alpha_param, target_p_uptake)
  beta_adverse_event <- calculate_beta(alpha_param, target_p_adverse_event)

  # Draw from Beta distributions for reached, uptake, and adverse event
  p_reached <- rbeta(n_simulations, alpha_param, beta_reached)
  n_reached <- round(population_size * p_reached)

  p_uptake <- rbeta(n_simulations, alpha_param, beta_uptake)
  n_uptake <- rbinom(n_simulations, n_reached, p_uptake)

  p_adverse_event <- rbeta(n_simulations, alpha_param, beta_adverse_event)
  n_no_intervention <- population_size - n_uptake
  adverse_events_no_intervention <- rbinom(n_simulations, n_no_intervention, p_adverse_event)

  # Effect size drawn from uniform distribution
  effect_size <- runif(n_simulations, effect_size_min, effect_size_max)

  # Adjusted adverse event rate for those who received the intervention
  adjusted_adverse_event_rate <- p_adverse_event * (1 - effect_size)
  adverse_events_with_intervention <- rbinom(n_simulations, n_uptake, adjusted_adverse_event_rate)

  # Total adverse events and cases prevented
  total_adverse_events <- adverse_events_no_intervention + adverse_events_with_intervention
  cases_prevented <- (n_uptake * p_adverse_event) - adverse_events_with_intervention

  # Store results in a data.table
  results_dt <- data.table(
    simulation_id = 1:n_simulations,
    effect_size,
    population_size,
    p_reached,
    n_reached,
    p_uptake,
    n_uptake,
    p_adverse_event,
    n_no_intervention,
    adverse_events_no_intervention,
    adjusted_adverse_event_rate,
    adverse_events_with_intervention,
    total_adverse_events,
    cases_prevented
  )

  # Convert to tibble for output
  results_tibble <- as_tibble(results_dt)

  # Combine results with input parameters
  output <- list(
    input_parameters = list(
      population_size = population_size,
      n_simulations = n_simulations,
      alpha_param = alpha_param,
      target_p_reached = target_p_reached,
      target_p_uptake = target_p_uptake,
      target_p_adverse_event = target_p_adverse_event,
      effect_size_min = effect_size_min,
      effect_size_max = effect_size_max,
      simulation_name = simulation_name
    ),
    simulation_results = results_tibble
  )

  # Save the combined output to cache
  saveRDS(output, cache_path)

  return(output)
}

summarize_simulation_results <- function(simulation_results) {
  simulation_results |>
    summarise(
      p025_cases_prevented = quantile(cases_prevented, 0.025),
      p05_cases_prevented = quantile(cases_prevented, 0.05),
      p10_cases_prevented = quantile(cases_prevented, 0.10),
      p25_cases_prevented = quantile(cases_prevented, 0.25),
      median_cases_prevented = median(cases_prevented),
      mean_cases_prevented = mean(cases_prevented),
      p75_cases_prevented = quantile(cases_prevented, 0.75),
      p90_cases_prevented = quantile(cases_prevented, 0.90),
      p95_cases_prevented = quantile(cases_prevented, 0.95),
      p975_cases_prevented = quantile(cases_prevented, 0.975),
      mean_effect_size = mean(effect_size),
      min_effect_size = min(effect_size),
      max_effect_size = max(effect_size)
    )
}

generate_simulation_plots <- function(simulation_results) {
  # Calculate rates
  simulation_results <- simulation_results %>%
    mutate(
      adverse_event_rate_no_intervention = adverse_events_no_intervention / n_no_intervention,
      adverse_event_rate_with_intervention = adverse_events_with_intervention / n_uptake
    )

  # Effect Sizes Plot
  effect_size_plot <- ggplot(simulation_results, aes(x = effect_size)) +
    geom_histogram(bins = 50, fill = 'skyblue', color = 'black') +
    labs(title = 'Distribution of Effect Sizes', x = 'Effect Size', y = 'Frequency') +
    theme_minimal()

  # Number Reached Plot
  n_reached_plot <- ggplot(simulation_results, aes(x = n_reached)) +
    geom_histogram(bins = 50, fill = 'skyblue', color = 'black') +
    labs(title = 'Distribution of ANC Patients Reached', x = 'Number Reached', y = 'Frequency') +
    theme_minimal()

  # Number Uptake Plot
  n_uptake_plot <- ggplot(simulation_results, aes(x = n_uptake)) +
    geom_histogram(bins = 50, fill = 'skyblue', color = 'black') +
    labs(title = 'Distribution of Number Participating In Intervention', x = 'Number Uptake', y = 'Frequency') +
    theme_minimal()

  # Adverse Events No Intervention (Counts)
  adverse_events_no_intervention_plot <- ggplot(simulation_results, aes(x = adverse_events_no_intervention)) +
    geom_histogram(bins = 50, fill = 'skyblue', color = 'black') +
    labs(title = 'Adverse Events (No Intervention)', x = 'Number of Adverse Events', y = 'Frequency') +
    theme_minimal()

  # Adverse Events With Intervention (Counts)
  adverse_events_with_intervention_plot <- ggplot(simulation_results, aes(x = adverse_events_with_intervention)) +
    geom_histogram(bins = 50, fill = 'skyblue', color = 'black') +
    labs(title = 'Adverse Events (With Intervention)', x = 'Number of Adverse Events', y = 'Frequency') +
    theme_minimal()

  # Combined Plot for Adverse Event Rates
  adverse_event_rates_combined <- simulation_results %>%
    select(adverse_event_rate_no_intervention, adverse_event_rate_with_intervention) %>%
    pivot_longer(cols = everything(), names_to = "intervention_status", values_to = "rate")

  adverse_event_rate_plot <- ggplot(adverse_event_rates_combined, aes(x = rate, fill = intervention_status)) +
    geom_histogram(bins = 50, position = "identity", alpha = 0.5, color = 'black') +
    scale_fill_manual(values = c('#1f77b4', '#ff7f0e'), labels = c('No Intervention', 'With Intervention')) +  # Blue and Orange
    labs(title = 'Comparison of Adverse Event Rates', x = 'Adverse Event Rate', y = 'Frequency') +
    theme_minimal()

  adverse_event_density_plot <- ggplot(adverse_event_rates_combined, aes(x = rate, fill = intervention_status)) +
  geom_density(alpha = 0.5, color = 'black') +
  scale_fill_manual(values = c('#1f77b4', '#ff7f0e'), labels = c('No Intervention', 'With Intervention')) +  # Blue & Orange
  labs(title = 'Comparison of Adverse Event Rates (Density Plot)',
       x = 'Adverse Event Rate',
       y = 'Density') +
  theme_minimal()

  # Cases Prevented Plot
  cases_prevented_plot <- ggplot(simulation_results, aes(x = cases_prevented)) +
    geom_histogram(bins = 50, fill = 'skyblue', color = 'black') +
    labs(title = 'Distribution of Cases Prevented', x = 'Cases Prevented', y = 'Frequency') +
    theme_minimal()

  # Quantiles for Cases Prevented
  cases_prevented_quantiles <- quantile(simulation_results$cases_prevented, probs = seq(0, 1, 0.05))

  # Return list of plots and quantiles
  list(
    effect_size_plot = effect_size_plot,
    n_reached_plot = n_reached_plot,
    n_uptake_plot = n_uptake_plot,
    adverse_events_no_intervention_plot = adverse_events_no_intervention_plot,
    adverse_events_with_intervention_plot = adverse_events_with_intervention_plot,
    adverse_event_rate_plot = adverse_event_rate_plot,
    adverse_event_density_plot = adverse_event_density_plot,
    cases_prevented_plot = cases_prevented_plot,
    cases_prevented_quantiles = cases_prevented_quantiles
  )
}

format_summary_results <- function(summary_results) {
  summary_results |>
    tidyr::pivot_longer(cols = everything(), names_to = "Metric", values_to = "Value") |>
    dplyr::mutate(
      Metric = dplyr::recode(Metric,
        p025_cases_prevented = "2.5th Percentile Cases Prevented",
        p05_cases_prevented = "5th Percentile Cases Prevented",
        p10_cases_prevented = "10th Percentile Cases Prevented",
        p25_cases_prevented = "25th Percentile Cases Prevented",
        median_cases_prevented = "Median Cases Prevented",
        mean_cases_prevented = "Mean Cases Prevented",
        p75_cases_prevented = "75th Percentile Cases Prevented",
        p90_cases_prevented = "90th Percentile Cases Prevented",
        p95_cases_prevented = "95th Percentile Cases Prevented",
        p975_cases_prevented = "97.5th Percentile Cases Prevented",
        mean_effect_size = "Mean Effect Size",
        min_effect_size = "Minimum Effect Size",
        max_effect_size = "Maximum Effect Size"
      )
    ) |>
    mutate(
      Value = round(Value, 2)
    )
}

format_quantiles_table <- function(quantiles_vector) {
  tibble::tibble(
    Quantile = names(quantiles_vector),
    Value = format(round(as.numeric(quantiles_vector), 2), scientific = FALSE)
  )
}

format_simulation_parameters <- function(parameters) {
  tibble::tibble(
    Parameter = names(parameters),
    Value = sapply(parameters, function(x) {
      if (is.numeric(x)) {
        format(x, scientific = FALSE)
      } else {
        as.character(x)
      }
    })
  )
}

output_simulation_results <- function(simulation_output, intervention_name = "Intervention") {

  # Format simulation parameters
  formatted_parameters <- format_simulation_parameters(simulation_output$input_parameters)

  # Display formatted simulation parameters
  cat(paste0("\n### Simulation Parameters\n"))
  print(formatted_parameters |> kable())

  # Summarize simulation results
  summary_results <- summarize_simulation_results(simulation_output$simulation_results)

  # Format summarized results
  formatted_results <- format_summary_results(summary_results)

  # Display formatted summary table
  cat(paste0("###  Summary Results\n"))
  print(formatted_results |> kable())
  # Generate plots
  sim_plots <- generate_simulation_plots(simulation_output$simulation_results)

  # Display key plots
  cat(paste0("\n### Plots\n"))
  print(sim_plots$n_reached_plot)
  print(sim_plots$n_uptake_plot)
  print(sim_plots$effect_size_plot)
  print(sim_plots$adverse_events_no_intervention_plot)
  print(sim_plots$adverse_events_with_intervention_plot)
  print(sim_plots$adverse_event_rate_plot)
  print(sim_plots$adverse_event_density_plot)
  print(sim_plots$cases_prevented_plot)

  # Format and display quantiles for cases prevented
  cat(paste0("\n\n### Cases Prevented Quantiles\n"))
  quantiles_table <- format_quantiles_table(sim_plots$cases_prevented_quantiles)
  print(quantiles_table |> kable())
}

```


```{r run_simulations, echo=FALSE}
n_simulations <- 3000000
n_population <- 422726
alpha_param <- 40


low_dose_aspirin_pe_simulation_results <- simulate_outcomes(
  population_size = n_population,
  n_simulations = n_simulations,
  alpha_param = alpha_param,
  target_p_reached = 0.145,
  target_p_uptake = 0.75,
  target_p_adverse_event = 0.06,
  effect_size_min = 0.10,
  effect_size_max = 0.24,
  simulation_name = "low_dose_aspirin_preeclampsia_simulation",
  attempt_cache = TRUE
)

low_dose_aspirin_eclampsia_simulation_results <- simulate_outcomes(
  population_size = n_population,
  n_simulations = n_simulations,
  alpha_param = alpha_param,
  target_p_reached = 0.145,         
  target_p_uptake = 0.75,           
  target_p_adverse_event = 0.015,   
  effect_size_min = 0.10,           
  effect_size_max = 0.24,
  simulation_name = "low_dose_aspirin_eclampsia_simulation",
  attempt_cache = TRUE
)

calcium_pe_simulation_results <- simulate_outcomes(
  population_size = n_population,
  n_simulations = n_simulations,
  alpha_param = alpha_param,
  target_p_reached = 1.00,
  target_p_uptake = 0.75,
  target_p_adverse_event = 0.15,
  effect_size_min = 0.40,
  effect_size_max = 0.60,
  simulation_name = "calcium_preeclampsia_simulation",
  attempt_cache = TRUE
)

mgso4_eclampsia_simulation_results <- simulate_outcomes(
  population_size = n_population,
  n_simulations = n_simulations,
  alpha_param = alpha_param,
  target_p_reached = 0.05,
  target_p_uptake = 0.65,
  target_p_adverse_event = 0.015,
  effect_size_min = 0.36,
  effect_size_max = 0.56,
  simulation_name = "mgso4_eclampsia_simulation",
  attempt_cache = TRUE
)

mms_anemia_simulation_results <- simulate_outcomes(
  population_size = n_population,
  n_simulations = n_simulations,
  alpha_param = alpha_param,
  target_p_reached = 1.00,
  target_p_uptake = 0.75,
  target_p_adverse_event = 0.40,
  effect_size_min = 0.17,
  effect_size_max = 0.37,
  simulation_name = "mms_anemia_simulation",
  attempt_cache = TRUE
)

mms_lbw_simulation_results <- simulate_outcomes(
  population_size = n_population,
  n_simulations = n_simulations,
  alpha_param = alpha_param,
  target_p_reached = 1.00,
  target_p_uptake = 0.75,
  target_p_adverse_event = 0.149,
  effect_size_min = 0.17,
  effect_size_max = 0.37,
  simulation_name = "mms_low_birth_weight_simulation",
  attempt_cache = TRUE
)

fcm_anemia_simulation_results <- simulate_outcomes(
  population_size = n_population,
  n_simulations = n_simulations,
  alpha_param = alpha_param,
  target_p_reached = 0.12,
  target_p_uptake = 0.85,
  target_p_adverse_event = 0.12,
  effect_size_min = 0.64,
  effect_size_max = 0.87,
  simulation_name = "fcm_anemia_simulation",
  attempt_cache = TRUE
)

```

# Results

For each intervention, we simulated the **reachable population**, **intervention uptake**, and **adverse event rates** based on available data. The primary variation across interventions lies in the **effect sizes**. Below, we provide the **median** and **10-90% credible intervals** for the number of **cases prevented**.

- **To estimate cost savings**, multiply the number of cases prevented by the cost per case.
- **To estimate mortality reductions**, apply the death rate per case to the number of cases prevented.

---

## Low-Dose Aspirin (Preeclampsia)

```{r output_results1, echo=FALSE, results='asis'}
output_simulation_results(low_dose_aspirin_pe_simulation_results, "Low-Dose Aspirin (Preeclampsia)")

```

## Low-Dose Aspirin (Eclampsia)

```{r output_results2, echo=FALSE, results='asis'}
output_simulation_results(low_dose_aspirin_eclampsia_simulation_results, "Low-Dose Aspirin (Eclampsia)")

```

## Calcium (Preeclampsia)

```{r output_results3, echo=FALSE, results='asis'}
output_simulation_results(calcium_pe_simulation_results, "Calcium (Preeclampsia)")

```

## MgSO₄ (Eclampsia)

```{r output_results4, echo=FALSE, results='asis'}

output_simulation_results(mgso4_eclampsia_simulation_results, "MgSO₄ (Eclampsia)")

```

## MMS (Anemia)


```{r output_results5, echo=FALSE, results='asis'}
output_simulation_results(mms_anemia_simulation_results, "MMS (Anemia)")

```

## MMS (Low Birth Weight)

```{r output_results6, echo=FALSE, results='asis'}
output_simulation_results(mms_lbw_simulation_results, "MMS (Low Birth Weight)")

```

## FCM (Anemia)

```{r output_results7, echo=FALSE, results='asis'}
output_simulation_results(fcm_anemia_simulation_results, "FCM (Anemia)")

```